### 2018-02-07 usenix18/pipe.tex

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. The following theorem states the correctness and security of
the scheme.

@@

\subsubsection*{Managing circuit sizes using partitioning}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.

>>>>

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. An example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

\paragraph{Security.} The following theorem states the correctness and security of
code partitioning.

@@

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work. \nc{I changed the heading.}
